---
title: "Chapter 10: Resampling for Evaluating Performance"
format: html
---

```{r, include=FALSE}
source("../ames_snippets.r")
```

You can evaluate a model on the test set, but this is not
recommended for models where you need to _tune_ your model
parameters — tuning params on the test set introduces _leakage_.
A better approach is to _resample_ your training set. Tidymodels
provides great functions for doing this.

Here, we fit a new model to the `ames` dataset: a random forest.
Notice that we start a new workflow object here:

```{r}
rf_model <- 
  rand_forest(trees = 1000) %>% 
  set_engine("ranger") %>% 
  set_mode("regression")

rf_wflow <- 
  workflow() %>% 
  add_formula(
    Sale_Price ~ Neighborhood + Gr_Liv_Area + Year_Built + Bldg_Type + 
      Latitude + Longitude) %>% 
  add_model(rf_model) 

rf_fit <- rf_wflow %>% fit(data = ames_train)
```

Now, compare the `lm` workflow agains the `ranger::random_forest` workflow with tidymodels:

```{r}
estimate_perf <- function(model, dat) {
    # Capture the names of the `model` and `dat` objects
    cl <- match.call()
    obj_name <- as.character(cl$model)
    data_name <- as.character(cl$dat)
    data_name <- gsub("ames_", "", data_name)

    reg_metrics <- metric_set(rmse, rsq)
      model %>%
    predict(dat) %>%
    bind_cols(dat %>% select(Sale_Price)) %>%
    reg_metrics(Sale_Price, .pred) %>%
    select(-.estimator) %>%
    mutate(object = obj_name, data = data_name)
}

bind_rows(list(Random_forest=estimate_perf(rf_fit, ames_train), LM=estimate_perf(lm_fit, ames_train)), .id="id")
```

So, Random Forest is clearly superior, right? Well, let's see
how it performs on the test set:

```{r}
estimate_perf(rf_fit, ames_test)
```

The RMSE is actually _higher_! How could this happen? Well,
in statistics, _low bias_ models perform great in training
but poorly in testing because they basically memorise the
training data. 

