---
title: "Ch. 5: Spending our Data"
format: html
---

When you start off modeling some data, you can potentially do
an infinite number of things to it e.g. parameter estimation,
model selection, tuning, performance QA, etc. However, if you
continuously do these tasks to any and all parts of your
data simultaneously, you will introduce _bias_ into the model
through leakage e.g. if you use some of your test data in
model parameter tuning. This chapter suggests setting a mental
heuristic for creating a data budget that you can spend.

A common first step is "splitting" data into a training and
testing set.

```{r, include=FALSE}
source("../ames_snippets.R")
```


Example using `rsample` to get an 80-20 split:

```{r}
library(tidymodels)
set.seed(501)

ames_split <- initial_split(ames, prop=.8)

ames_split

```

Use the functions below to get your data into split dfs:

```{r}
ames_train <- training(ames_split)
ames_test <- testing(ames_split)
```

In the case of classification with imbalanced classes,
stratified classification can be used to do splitting
separately for each class and then combining the result.
For regression, a similar approach is to stratify by
quantiles:

```{r}
qs <- quantile(ames$Sale_Price)[2:4]
ames %>%
    ggplot(aes(x=Sale_Price)) +
        geom_histogram(bins=50) +
        geom_vline(xintercept = qs, lty="dashed")

```

Within each, it will run the sampling for train and test :)

```{r}
ames_split <- initial_split(ames, prop = 0.80, strata = Sale_Price)
ames_train <- training(ames_split)
ames_test  <-  testing(ames_split)

dim(ames_train)
```

::: {.callout-tip}
There is very little downside to using stratified sampling
:::

Note that for time series data, you can use `initial_time_split()`
to create a train test split; this assumes that you want later
data to be forecasted and earlier data to be the training data.

It's also important to separate your notion of a test set from
a validation set. A _validation_ set is what you use to
_validate your training models_, i.e. you use it to tune
parameters. A test set must remain an unbiased (unseen) data
set that the final model is evaluated on.

### Multilevel Modeling

When data points in the outcome are structurally or conceptually
related to each other, this might be a case for multilevel
modeling. e.g. longitudinal data where one participant has
multiple time points/repeated measures (or a mobile phone study where one participant has many EMA responses 😉)

### Other considerations

- keep your test set _far away_ from your training set
- no matter your operations on the data, keep your
test set as close to real world data as possible
- These considerations are for training and evaluation of the model; once you know the model is the best it can be,
you are free to use the full dataset to productionize 
the model

