---
title: "Ch. 4: Introduction to Ames Housing Data"
format: html
---

Load the data

```{r}
library(modeldata)

data(ames)
```

## Some EDA

First examine the outcome variable:

```{r}
library(tidymodels)

ames %>%
    ggplot(aes(x=Sale_Price)) +
        geom_histogram(bins=50)
```

What are the quantiles and median?

```{r}
summary(ames$Sale_Price)
```

Show median:

```{r}
ames %T>%
    {m <<- .$Sale_Price %>% median() } %>%
    ggplot() +
        geom_histogram(aes(x=Sale_Price), bins=50) +
        geom_vline(xintercept = m, colour = "red")
```

Right skewed outcome, so log transforming will be recommended:


```{r}
ames %>%
    ggplot(aes(x=Sale_Price)) +
        geom_histogram(bins=50) +
        scale_x_log10()
```

More normal, but with the disadvantage that interpretability may be lost.

```{r}
# move forward with this decision
ames <- ames %>% mutate(Sale_Price = log10(Sale_Price))
```

Here's a quick EDA checklist:

1. Identify the outcome variable
    - What kind of distribution does it have? Is the distribution appropriate for modeling/ML?
    - If categorical, are the classes balanced?
    - Is it skewed?
    - Are there outliers? How severe are they?
2. For each predictor variable:
    - What kind of distribution does it have/what is the count of categories?
    - Do predictors autocorrelate?
    - Does the predictor correlate with the outcome?
